# In-Class Programming Activity, Day 10

###Nadia Berriel 

# In-Class Programming Activity, Day 10

```{r}
library(ISLR)
```
## Logistic Function

```{r}
logistic <- function(x){
  result <- exp(x)/(1+exp(x))
  return(result)
}
```

## Linear Combination

A function to calculate linear combinations of variables in a given dataset.

```{r}
linear_combine <- function(coefs, data){
  result <- 0
  for (nm in names(coefs)){
    if (nm == "intercept"){
      result <- result + coefs[[nm]]
    }else if (is.null(data[[nm]])){
      stop()
    }else {
      result <- result + coefs[[nm]] * data[[nm]]
    }
  }
  return (result)
}

head(linear_combine(data = Default, coefs = c(intercept=3, balance=0.00001, income=-0.0002)))
```


## Probabilities

A logistic function that computes log-likelihood of the data given the coefficients

```{r}
LL_logistic <- function(coefs, data,  outcome){
  result_1 <- linear_combine(data = data, coefs = coefs)
  result_2 <- logistic(result_1)
  likelihood <- ifelse(outcome == TRUE, result_2, 1-result_2)
  log_likelihood <- sum(log(likelihood))
  return (log_likelihood)
}

LL_logistic(data=Default, 
            coefs = c(intercept = 1, income = -0.0001), 
            outcome = Default$default == "Yes")

```

## Optimize

```{r}
starting_params <- c(intercept =1, income=-0.0001)
best_coefs <- optim(starting_params, LL_logistic, data=Default, outcome=Default$default=="Yes", control = list(fnscale = -1))
best_coefs

glm(default == "Yes" ~ income, data=Default, family="binomial")
```

The two functions give similar estimates of intercept and coeficient of income.

## Above and Beyond
```{r}
LL_logistic <- function(data=NULL, coefs=NULL, outcome){
  outcome_statement <- substitute(outcome)
  outcome <- eval(outcome_statement, envir = data)
  result_1 <- linear_combine(data = data, coefs = coefs)
  result_2 <- logistic(result_1)
  likelihood <- ifelse(outcome == TRUE, result_2, 1-result_2)
  log_likelihood <- sum(log(likelihood))
  return (log_likelihood)
}

LL_logistic(data=Default, 
            coefs = c(intercept = 1, income = -0.0001), 
            outcome = default == "Yes")
```

## Test statements

```{r}
scoreActivity::score253(10)
```