# In-Class Programming Activity, Day 11

###Nadia Berriel

## The covariance matrix

```{r}
Sigma <- matrix(c(1.0,-0.7,-0.7,1), nrow = 2, ncol=2)
Sigma_inv <- solve(Sigma)
test_inverse <- Sigma %*% Sigma_inv
```

## Matrix composition

```{r}
A <- chol(Sigma)
A
t(A)
t(A)%*%A
```

## Orthogonal vectors and matrices
```{r}
x1 <- rnorm(10)
x2 <- rnorm(10)
inner <- sum(x1*x2)
```

Two vectors in matrix form
```{r}
x1 <- cbind(x1) #can I use as.matrix?
x2 <- cbind(x2)
inner <- t(x1) %*% x2
```

```{r}
X <- cbind(x1,x2)
X_cov <- t(X) %*% X / nrow(X)
X_cov
```

Do the same for W with length 10,000
```{r}
w1 <- rnorm(10000)
w2 <- rnorm(10000)
W <- cbind(w1, w2)
W_cov <- t(W) %*% W / nrow(W)
W_cov
```
Covariance matrix very close to diagnal because two random vectors are almost uncorrelated.

## Getting correlated random vectors
```{r}
A_inv <- chol(Sigma_inv)
Y <- X %*% A
```

```{r}
Y <- W %*% A
Y_cov <- t(Y) %*% Y / nrow(Y)
Y_cov
Sigma
1/sqrt(nrow(Y))
```

The covariance matrix of new Y is very close to Sigma. The difference is very close to 0.01.

Plot the multivariate Gaussiann distribution with covariance A

```{r}
plot(Y[,1], Y[,2], col=rgb(0,0,0,.05))
```

The plot shows that first and second columns of Y are correlated (stretched oval shape).

## Test statements

```{r}
scoreActivity::score253(11)
```