# In-Class Programming Activity, Day 15

#Nadia Berriel

Make input matrix X (191 columns and 250 row in this case for Mona Lisa)
```{r}
load("mona.rda")
X <- t(mona) - mean(mona[]) #monochrome version of Mona Lisa
X_rand <- matrix(rnorm(191*250), nrow = 250, ncol = 191) #random iid noise
X_corr <- X_rand %*% chol(var(X)) #correlated noise
```

###Sparse data

```{r}
beta <- rep(0, 191)
inds <- sample(1:191, size=16)
beta[inds[1:4]] = 2
beta[inds[5:8]] = 5
beta[inds[9:12]] = -3
beta[inds[13:16]] = -5
```

###The output

```{r}
Y_pure <- X %*% beta
Y_real <- Y_pure + rnorm(250, mean=0, sd=sqrt(0.1*var(Y_pure)))
```


###Least squares

```{r}
mod_pure <- lm(Y_pure ~ X)
beta_hat_pure <- coef(mod_pure)[-1]
plot(beta, beta_hat_pure)
mod_real <- lm(Y_real ~ X)
beta_hat_real <- coef(mod_real)[-1]
plot(beta, beta_hat_real)
```

Many coefficients that should be 0 are not 0 in beta_hat_real. So can't really tell beta is sparse from beta_hat_real.

###The Lasso

```{r}
library(glmnet)
lasso_mod <- cv.glmnet(X, Y_real, alpha=1)
beta_lasso <- predict(lasso_mod, type = "coefficients", s=lasso_mod$lambda.min)
plot(beta, beta_lasso[-1])
```

Fewer coefficients that are off at 0.

###Principal components

```{r}
sing_vals_X <- svd(X)$d
sing_vals_Xrand <- svd(X_rand)$d
sing_vals_Xcorr <- svd(X_corr)$d
R_X <- cumsum(sing_vals_X^2)/sum(sing_vals_X^2)
R_Xrand <- cumsum(sing_vals_Xrand^2)/sum(sing_vals_Xrand^2)
R_Xcorr <- cumsum(sing_vals_Xcorr^2)/sum(sing_vals_Xcorr^2)
k <- seq(1,191)
Prin_Comp <- data.frame(cbind(k, R_X, R_Xrand, R_Xcorr))
library(tidyr)
library(ggplot2)
Prin_Comp_data <- gather(Prin_Comp, key=data, value=r_sqr, -k)
ggplot(Prin_Comp_data, aes(k, r_sqr)) + geom_point(aes(colour=data))
n99 <- Prin_Comp[R_X >=0.99,][1,1]
n99_rand <- Prin_Comp[R_Xrand >=0.99,][1,1]
n99_corr <- Prin_Comp[R_Xcorr >=0.99,][1,1]
```


```{r}
library(pls)
pcr.fit <- pcr(Y_real ~ X, scale = T, validation="CV")
R2(pcr.fit)
```

After 50 components, R^2 comes closest to 0.85. However, after 14 components there doesn't seem to be much increase.







## Test statements

```{r}
scoreActivity::score253(15)
```