# In-Class Programming Activity, Day 16

```{r}
library(ISLR)
```

## The Knots
Write function my_knots
```{r}
my_knots <- function(x, k) {
  knots <- numeric(k)
  for (i in 1:k){
    knots[i] <- quantile(x, i/(k+1))
  }
  return(knots)
}
```

## The basis set
Write a function to calculate model matrix for x and knot locations
```{r}
spline_model_matrix <- function(x, knot_locations) {
  MM <- cbind(1, x, x^2, x^3)
  for (i in 1:length(knot_locations)){
    new_v <- ifelse(x>knot_locations[i], (x-knot_locations[i])^3,0)
    MM <- cbind(MM, new_v)
  }
  return(MM)
}
```

## Finding the best linear computation
```{r}

fit_spline <- function(formula, k=2, data=parent.frame()){
  y <- eval(formula[[2]], envir=data)
  x <- eval(formula[[3]], envir=data)
  knot_locations <- my_knots(x,k)
  MM <- spline_model_matrix(x, knot_locations)
  mod <- lm(y~ MM - 1)
  res <- list(coef = coef(mod), knots = knot_locations, cov=vcov(mod), rse=summary(mod)$sigma)
  class(res) <- "my_spline"
  
  return(res)
}
```

## The predict function

```{r}
predict.my_spline <- function(mod, newx, level= 0.95, intervals=c("none","confidence","prediction")) {
  intervals <- match.arg(intervals)
  MM <- spline_model_matrix(newx, mod$knots)
  vals <- MM %*% mod$coef
  se <- sqrt(rowSums(MM %*% mod$cov * MM))
  if (intervals == "none") return(vals)
  else return(NULL)
}
```

```{r}
mod <- fit_spline(wage~age, data = Wage) # Return 2 values ??
mod_pred <- predict(mod,newx=Wage$age, intervals="none") 
library(ggplot2)
ggplot(Wage, aes(age,wage)) + geom_point(aes(alpha=1/10)) + geom_smooth(aes(age,mod_pred))
```

## Confidence intervals

```{r}
predict.my_spline <- function(mod, newx, level= 0.95, intervals=c("none","confidence","prediction")) {
  intervals <- match.arg(intervals)
  MM <- spline_model_matrix(newx, mod$knots)
  vals <- MM %*% mod$coef
  se <- sqrt(rowSums(MM %*% mod$cov * MM))
  if (intervals == "none") return(vals)
  else if (intervals == "confidence"){
    upper <- vals + 2*se
    lower <- vals - 2*se
    return(data.frame(vals=vals, upper=upper, lower=lower))
  }
  else return(NULL)
}
```

Graph the predicted splines

```{r}
mod_pred <- predict(mod,newx=Wage$age, intervals="confidence")
ggplot(Wage, aes(age,wage)) + geom_point(aes(alpha=1/10)) + geom_smooth(aes(age,mod_pred$vals)) + geom_smooth(aes(age, mod_pred$upper, colour="red")) + geom_smooth(aes(age, mod_pred$lower, colour="red"))
```

## Prediction intervals (Is this correct???)
```{r}
predict.my_spline <- function(mod, newx, level= 0.95, intervals=c("none","confidence","prediction")) {
  intervals <- match.arg(intervals)
  MM <- spline_model_matrix(newx, mod$knots)
  vals <- MM %*% mod$coef
  se <- sqrt(rowSums(MM %*% mod$cov * MM))
  if (intervals == "none") return(vals)
  else if (intervals == "confidence"){
    upper <- vals + 2*se
    lower <- vals - 2*se
    return(data.frame(vals=vals, upper=upper, lower=lower))
  }
  else if (intervals == "prediction"){
    se_pred <- sqrt(se^2 + mod$rse^2)
    lower <- vals - 2*se_pred
    upper <- vals + 2*se_pred
    return(data.frame(lower=lower, vals=vals, upper=upper))
  }
  else return(NULL)
}
```

```{r}
mod <- fit_spline(wage~age, data = Wage)
mod_pred <- predict(mod,newx=Wage$age, intervals="prediction")
ggplot(Wage, aes(age,wage)) + geom_point(aes(alpha=1/10)) + geom_smooth(aes(age,mod_pred$vals)) + geom_smooth(aes(age, mod_pred$upper, colour="red")) + geom_smooth(aes(age, mod_pred$lower, colour="red"))
```


Difference between confidence interval and prediction intervals?

## How many knots?
```{r}
knots <- c(2,5, 10,20)
for (k in knots){
  mod <- fit_spline(wage~age, data=Wage, k=k)
  mod_pred <- predict(mod, newx = Wage$age, interval="none")
  print(mean((Wage$wage - mod_pred)^2))
}
```

As number of knots increases, the model fits the data more closely.

```{r}
set.seed(6)
trains <- sample(1:nrow(Wage), nrow(Wage)/2)
Train <- Wage[trains,]
Test <- Wage[-trains,]

knots <- seq(2,20,1)
mse <- numeric(length(knots))
for (i in 1:length(knots)){
  mod <- fit_spline(wage~age, data=Train, k=knots[i])
  mod_pred <- predict(mod, newx = Test$age, interval="none")
  mse[i] <- mean((Test$wage - mod_pred)^2)
}

plot(knots, mse)
```

Around 5 knots.


## Test statements

```{r}
scoreActivity::score253(16)
```