# In-Class Programming Activity, Day 17

###NADIA BERRIEL


## Growing and Pruning Tree
```{r}
Cartoon_data <- data.frame(
  x = 1:8,
  y = c(2,5,1,3,8,5,4,6),
  class = c("A","B","A","A","B","B","A","B")
) 

library(tree)
```

## Perfectly pure tree
```{r}
pure <- tree.control(8, mincut = 0, minsize = 1, mindev = 0) #what is this?
```

## Regression tree
```{r}
rtree_pure <- tree(y ~ x, data=Cartoon_data, control = pure)
plot(rtree_pure)
text(rtree_pure)
```

The output for x=3 is 1

## Classification tree
```{r}
ctree_pure <- tree(class~x, data=Cartoon_data, control = pure)
plot(ctree_pure)
text(ctree_pure)
```

The output for x=7 is A

## Evaluating the tree
```{r}
predict(rtree_pure)
predict(ctree_pure)
predict(rtree_pure, newdata = data.frame(x=3))
predict(ctree_pure, newdata = data.frame(x=7))
```

## Deviance of each node
```{r}
print(ctree_pure)
print(rtree_pure)
```

The deviance each node eliminates, regression tree:
4.5: 18
2.5: 2.25
1.5: 4.5
3.5: 2
5.5: 6.75
7.5: 1.5
6.5: 0.5

Classification tree:
4.5: 2.11
2.5: 1.29
6.5: 1.79
1.5: 2.7
7.5: 2.7

## Deviance of a tree
```{r}
rtree_pred <-predict(rtree_pure, newdata = Cartoon_data)
rtree_devi <- sum((Cartoon_data$y - rtree_pred)^2) #equals 0

```

## Pruning the tree
```{r}
rtree_5 <- prune.tree(rtree_pure, best=5)
ctree_2 <- prune.misclass(ctree_pure, best=2)
dev_vs_nodes <- function(nnodes) {
  pruned <- prune.tree(rtree_pure, best = nnodes)
  deviance(pruned)
}
nterminal <- 2:8
tree_deviance <- sapply(nterminal, FUN = dev_vs_nodes)
plot(nterminal, tree_deviance)
```

## Building a real clasifier
```{r}
library(mosaicData)
pure_for_cps <- tree.control(nrow(CPS85), mincut=0, minsize = 1, mindev = 0)
Sector_classifier <- tree(sector~wage+sex+educ+exper, data=CPS85, control=pure_for_cps)
tree_prune <- prune.misclass(Sector_classifier,best=20)
deviance(tree_prune)
plot(tree_prune)
text(tree_prune)

tree_cv <- cv.tree(Sector_classifier, FUN=prune.misclass) #6 gives the best test error
tree_prune_2 <- prune.misclass(Sector_classifier, best=6)
deviance(tree_prune_2)
plot(tree_prune_2)
text(tree_prune_2)
```


## Test statements

```{r}
scoreActivity::score253(17)
```