## Math 365 / Comp 365: Midterm 2
## Take-Home Portion
### **Due Tuesday, April 11, 2017 at 8AM on Moodle**
#### *Please bring a stapled hard copy of your answers to class on Tuesday*
#### *Don't forget to sign and attach the cover sheet or copy the honor statement and sign electronically here*

### *NADIA BERRIEL*

The following line sources functions from the class file `365Functions.r`. Feel free to use any of these functions.
```{r,message=FALSE,warning=FALSE}
require(Matrix)
require(ggplot2)
require(tidyr)
source("https://www.macalester.edu/~dshuman1/data/365/365Functions.r")
source("https://www.macalester.edu/~dshuman1/data/365/panera.prices.r")
```

## Problem 5

Here is a plot of the data we have. Note: the prices are stored in `samp.prices`.

```{r}
days = 0:250 
samp.days = seq(0,250,by=10) # we only have data on these days
plot(samp.days,samp.prices,pch=20,cex=.5,ylim=c(180,280),
     ylab = "PNRA Closing Price",
     xlab = "Consecutive trading days up to 3/31/17",
     main = "Panera Stock Prices")
points(samp.days,samp.prices,pch=20,cex=1,col='red')
grid()
```

Here is the function we are going to use to plot the different interpolations and regression models:
```{r}
plotApproximations=function(f){
  tt = seq(0,250,length=1001)
  plot(tt,f(tt),col="DarkOrange",type='l',lwd=2,ylim=c(180,280),
       ylab = "PNRA Closing Price",
       xlab = "Consecutive trading days up to 3/31/17",
       main = "Panera Stock Prices")
  points(days,f(days),pch=20,cex=1,col='black') # The points guessed by the interpolating/regressing functions
  points(samp.days,samp.prices,pch=20,cex=1,col='red') # The sample points we have from every 10th day
}  
```


#### Part a: Polynomial Interpolation

```{r}
p <- function(){
  plot(x,y,pch=19,col='dodger')
}

plotApproximations(p)
```

#### Part b: Natural Cubic Spline


```{r}
sp <- function(){
  # I am using the line and spline function to draw the lines between the data points.
  lines(spline(samp.days,samp.prices, n = 1000, method = 'natural'), col='seagreen4')
}

plotApproximations(sp)
```

#### Part c: Linear Regression



```
Do some computations here to compute a function `f` that is your regression line
```

Then call this function to plot the given data and your regression line:
```
plotApproximations(f)
```

#### Part d: Compute the Errors
















## Problem 6

### Part a: Monomials

```{r}
y<-function(t){2*cos(4*t)}
tt<-seq(0,pi/2,length=1000)
```

#### Part i
```
N<-4
A<-
b<-
print(A)
print(b)
```

#### Part ii
```
y.approx<-function(t){
# fill in code here
}
plot(tt,y(tt),type='l',col="blue",lwd=3,ylab = "y(t)",xlab="t")
lines(tt,y.approx(tt),type='l',col="red",lwd=3)
grid()
```

#### Part iii: experiment with different values of N

### Part b: Piecewise-Linear B-Splines
