## Math 365 / Comp 365: Midterm 2
## Take-Home Portion
### **Due Tuesday, April 11, 2017 at 8AM on Moodle**
#### *Please bring a stapled hard copy of your answers to class on Tuesday*
#### *Don't forget to sign and attach the cover sheet or copy the honor statement and sign electronically here*

### *NADIA BERRIEL*

The following line sources functions from the class file `365Functions.r`. Feel free to use any of these functions.
```{r,message=FALSE,warning=FALSE}
require(Matrix)
require(ggplot2)
require(tidyr)
source("https://www.macalester.edu/~dshuman1/data/365/365Functions.r")
source("https://www.macalester.edu/~dshuman1/data/365/panera.prices.r")
```

## Problem 5

Here is a plot of the data we have. Note: the prices are stored in `samp.prices`.

```{r}
days = 0:250 
samp.days = seq(0,250,by=10) # we only have data on these days
plot(samp.days,samp.prices,pch=20,cex=.5,ylim=c(180,280),
     ylab = "PNRA Closing Price",
     xlab = "Consecutive trading days up to 3/31/17",
     main = "Panera Stock Prices")
points(samp.days,samp.prices,pch=20,cex=1,col='red')
grid()
```

Here is the function we are going to use to plot the different interpolations and regression models:
```{r}
plotApproximations=function(f){
  tt = seq(0,250,length=1001)
  plot(tt,f(tt),col="DarkOrange",type='l',lwd=2,ylim=c(180,280),
       ylab = "PNRA Closing Price",
       xlab = "Consecutive trading days up to 3/31/17",
       main = "Panera Stock Prices")
  points(days,f(days),pch=20,cex=1,col='black') # The points guessed by the interpolating/regressing functions
  points(samp.days,samp.prices,pch=20,cex=1,col='red') # The sample points we have from every 10th day
}  
```


#### Part a: Polynomial Interpolation

```{r}
#p <- function(){
#  lines(samp.days[order(samp.days)],samp.prices[order(samp.days)],xlim=range(samp.days),ylim=range(samp.prices), pch=16)
#}

#plotApproximations(p)
#Error in f(tt): unused argument (tt)
```

#### Part b: Natural Cubic Spline


```{r}
#sp <- function(){
  # I am using the line and spline function to draw the lines between the data points.
  #lines(spline(samp.days,samp.prices, n = 1000, method = 'natural'), col='seagreen4')
#}

#plotApproximations(sp)
#Error in f(tt): unused argument (tt)

```

#### Part c: Linear Regression

```{r}
#Do some computations here to compute a function `f` that is your regression line
#Then call this function to plot the given data and your regression line:

#I do not know how to fit a regression line 
#f <- function(){
  #plot(samp.days,samp.prices)
  #fit <- lm(samp.prices ~ samp.days)
  #abline(fit)
#}

#plotApproximations(f)
```

#### Part d: Compute the Errors

In order to compute the squared error we need to 1) Find the regression line, 2) Insert your X values into the linear regression equation to find the new Y values (Y'), 3) Subtract the new Y value from the original to get the error, 4) Square the errors, 5) Add up the errors, and then 6) Find the mean.

```{r}
#lm <- lm(samp.prices ~ samp.days)
#sm <- summary(lm)
#sm

#lm2 <- lm(all.prices ~ samp.days)
#sm2 <- summary(lm2)
#sm2
```

The Least Square method provides the best fit for the data.




## Problem 6

### Part a: Monomials

```{r}
y<-function(t){2*cos(4*t)}
tt<-seq(0,pi/2,length=1000)
```

#### Part i
```{r}
#added all the linear equations in 5,6,7.
y0 <- function(j){sum(cj* 0^(j-1),1,N)}
ypi <- function(j){sum(cj(pi/2)^(j-1))}
con <- function(j){sum(cj*((j-1)*(j-2)*t^(j-3)+16*t^(j-1)))}
N<-4
A<- matrix(c(y0,ypi,con))
b<- c(0,pi/2)
print(A)
print(b)
```

#### Part ii
```{r}
#I couldn't figure out how to do Part a, so now I can't do part b. I don't think I am suppose to use the sum() and probably didn't need to write out the functions. Would I have to use the funcitons 1,2, and 3 then?
y.approx<-function(t){
  #
}
plot(tt,y(tt),type='l',col="blue",lwd=3,ylab = "y(t)",xlab="t")
lines(tt,y.approx(tt),type='l',col="red",lwd=3)
grid()
```

### Part b: Piecewise-Linear B-Splines
```{r}
##First I would have to find the matrix A and values for b. 
#a <- function(h){(-32/3)*h + (2/h)}
#B <- function(h){(-8/3)*h - (1/h)}
#diag(a) # for the matrix


```










